---
title: "How to show relative frequencies in a histogram"
output: html_notebook
---

Often we want to visualize the frequencies of our histogram in relative terms
rather than absolute numbers. This feature is specially useful when we don't
know the size of our dataset or when we want to compare histograms of samples of
different sizes. In this post we are going to learn how to show in the histogram
the relative frequencies of the distribution.

First, let's take a look on the absolute frequencies of the Petal
Length attribute of the Iris dataset: 

```{r}
hist(iris$Petal.Length, col = '#FFE0B2', ylim=c(0,40), labels = TRUE)
```

In this plot we can observe the exact count of samples in each bin of the 
histogram. But if instead of the exact count, we would like to know how much
of the total each bar represents ?

We have two options to achieve this result. The first one is to set the
parameter **freq** to **FALSE**:

```{r}
hist(
  scale(iris$Petal.Length),
  col = '#FFE0B2',
  labels = TRUE,
  freq = FALSE
)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
