---
title: "How to Build Histograms with R"
output:
  html_document: default
  html_notebook: default
---

The histogram is one of the simplest and most useful data visualization tools.
Given a continous variable, it shows how its values are distributed along their
range. By visualizing the histogram, we can identify in a glimpse if a variable
is uniformly distributed or if a specific range of values concentrate most of
the ocurrences.

In this post, I am going to show how to build a histogram using the R basic
graph library. As example, we are going to use the Iris dataset, composed by 4
numeric attributes and a category attribute. We're going to build a histogram
for each one of its numeric attributes and explore some functionalities of the
R basic graphs system. 

We start our analysis by taking a quick look at some lines of the dataset and
summarizing the dataset:

```{r}
head(iris, n=10)
summary(iris)
```


The four attributes which represents the characteristics of the data instances
are continoues real numbers. In the summary we can observe the range of their
values, their mean and other position parameters. The category attribute is a
factor, and we observe that that dataset instances are equaly divided between
the three possible categories.

So, let's build our first histogram. We choose the attribute "Sepal.Length" to
begin:

```{r}
hist(iris$Sepal.Length)
```

And that's it! All you need to do is to call the function **hist** passing your 
data as argument and your histogram is ready. The **hist** function plots a 
histogram using default values for graphs and automatically calculates the
ranges of X and Y axes as well as the width, height and number of the bars.
Although the default behavior of the **hist** function provides us with a good
visualization of our data, we can easily customize this behavior to better fit
our needs. In the next subsections, we are going to explore some of the many
possibilities of customization of the histogram.

##Adding colors to the bars

In order to be effective, data visualization must be pleasant. Let's be honest,
nobody would pay attention to a bunch of lines, so coloring your histograms is
essential! In order to fill the histogram bars with colors we must add the 
**col** parameter in the **hist** function call:

```{R}

```


##How to label the bars

By viewing the histogram produced in the previous section we can observe that
nearly 30 instances of data have a Sepal Length between 5.5 and 6. But we would
like to know the exact count for this interval without appealing to a auxiliar
table. How can we achieve this ? By setting the **labels** parameter, let's
see:

```{R}
hist(iris$Sepal.Length, labels = T)
```




